---
title: "DCM summary results"
author: "Aniol Santo Angles"
date: "November 2022"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 5
    toc_float: yes

---
  
```{r, echo=FALSE, message=FALSE}
library(kableExtra)
library(rmatio)
library(ggcorrplot)

```

```{r, echo=FALSE, message=FALSE}

threshold_peb = 0.85

```

Manuscript figures with PEB results were created with  the present summary of results. Here, PEB results are presented in matrix form (rows as target region, columns as source region). Colored squares in matrix signal those connections with posterior probability Pp > 0.85. Red (blue) square means condition 1 higher (lower) than condition 2 (e.g., delay vs baseline, or correct vs swap). Quantitative information about PEB is presented in table with the following columns: Parameter (in column form described above), Ep (PEB parameter),	Pp (posterior probability). Brain regions: SFG, superior frontal gyrus; cMFG, contralateral middle frontal gyrus; iMFG ipsilateral middle frontal gyrus; cLIP, contralateral lateral intraparietal; iLIP, ipsilateral lateral intraparietal; cEVC, contralateral early visual cortex; iEVC ipsilateral early visual cortex. Contralateral (ipsilateral) relative to stimulus presentation. 


# within-trialtype PEB

## early delay vs baseline

```{r echo=FALSE, message=FALSE}

first_time = 'early_delay'
second_time = 'baseline'
times = c(first_time, second_time)

```

### highaccuracy

```{r echo=FALSE, message=FALSE}

trialtype = 'highaccuracy'

# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype,'_', first_time, '_vs_', second_time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```







### lowaccuracy

```{r echo=FALSE, message=FALSE}

trialtype = 'lowaccuracy'

# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype,'_', first_time, '_vs_', second_time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```






### swap

```{r echo=FALSE, message=FALSE}

trialtype = 'swap'

# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype,'_', first_time, '_vs_', second_time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```








## late delay vs baseline

```{r echo=FALSE, message=FALSE}

first_time = 'late_delay'
second_time = 'baseline'
times = c(first_time, second_time)

```

### highaccuracy

```{r echo=FALSE, message=FALSE}

trialtype = 'highaccuracy'

# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype,'_', first_time, '_vs_', second_time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```







### lowaccuracy

```{r echo=FALSE, message=FALSE}

trialtype = 'lowaccuracy'

# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype,'_', first_time, '_vs_', second_time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```






### swap

```{r echo=FALSE, message=FALSE}

trialtype = 'swap'

# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype,'_', first_time, '_vs_', second_time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table

kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```








# between-trialtype PEB

## baseline

```{r echo=FALSE, message=FALSE}

time = 'baseline'

```

### highaccuracy vs lowaccuracy

```{r echo=FALSE, message=FALSE}

trialtype_1 = 'highaccuracy'
trialtype_2 = 'lowaccuracy'


# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype_1, '_', trialtype_2, '_', time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```


### highaccuracy vs swap

```{r echo=FALSE, message=FALSE}

trialtype_1 = 'highaccuracy'
trialtype_2 = 'swap'


# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype_1, '_', trialtype_2, '_', time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```








### lowaccuracy vs swap

```{r echo=FALSE, message=FALSE}

trialtype_1 = 'lowaccuracy'
trialtype_2 = 'swap'


# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype_1, '_', trialtype_2, '_', time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```









## early_delay

```{r echo=FALSE, message=FALSE}

time = 'early_delay'

```

### highaccuracy vs lowaccuracy

```{r echo=FALSE, message=FALSE}

trialtype_1 = 'highaccuracy'
trialtype_2 = 'lowaccuracy'


# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype_1, '_', trialtype_2, '_', time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```


### highaccuracy vs swap

```{r echo=FALSE, message=FALSE}

trialtype_1 = 'highaccuracy'
trialtype_2 = 'swap'


# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype_1, '_', trialtype_2, '_', time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```








### lowaccuracy vs swap

```{r echo=FALSE, message=FALSE}

trialtype_1 = 'lowaccuracy'
trialtype_2 = 'swap'


# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype_1, '_', trialtype_2, '_', time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```








## late_delay

```{r echo=FALSE, message=FALSE}

time = 'late_delay'

```

### highaccuracy vs lowaccuracy

```{r echo=FALSE, message=FALSE}

trialtype_1 = 'highaccuracy'
trialtype_2 = 'lowaccuracy'


# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype_1, '_', trialtype_2, '_', time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```


### highaccuracy vs swap

```{r echo=FALSE, message=FALSE}

trialtype_1 = 'highaccuracy'
trialtype_2 = 'swap'


# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype_1, '_', trialtype_2, '_', time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```








### lowaccuracy vs swap

```{r echo=FALSE, message=FALSE}

trialtype_1 = 'lowaccuracy'
trialtype_2 = 'swap'


# load peb
peb = read.mat(paste('/Users/as14864/Data/Analysis/BESM/DCM/dcm_github_hbm/PEB/PEB_', trialtype_1, '_', trialtype_2, '_', time, '.mat', sep = ""))$PEB

# reset
peb$Ce = peb$Ce[[1]]
peb$Ep = peb$Ep[[1]]
peb$Pp = peb$Pp[[1]]

```

#### feedforward

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 1
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)

# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[2,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[3,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,4] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[2,4] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[1,5] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[3,5] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[1,6] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[2,6] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[4,6] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[1,7] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[3,7] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[5,7] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

#### feedback

```{r echo=FALSE, message=FALSE}

number_parameters = 113
firt_param = number_parameters + 19
number_parameters_matrix = 18 # matrices: A1, A2, AN1, AN2 (AMPA feedforward,...)
last_param = firt_param+number_parameters_matrix
index_param = firt_param:(last_param-1)
  
# output
param_table = as.data.frame(matrix(nrow = 0, ncol = 3))
colnames(param_table) = c("Parameter", "Ep", "Pp")

data_plot = as.data.frame(matrix(0, nrow = 7, ncol = 7))

# for each parameter
for (param_i in index_param) {
  
  # if Pp > threshold_peb
  if (peb$Pp[param_i] >= threshold_peb) {
    
    if (param_i == index_param[1]) {
      data_plot[4,1] = peb$Ep[param_i]
    } else if (param_i == index_param[2]) {
      data_plot[5,1] = peb$Ep[param_i]
    } else if (param_i == index_param[3]) {
      data_plot[6,1] = peb$Ep[param_i]
    } else if (param_i == index_param[4]) {
      data_plot[7,1] = peb$Ep[param_i]
    } else if (param_i == index_param[5]) {
      data_plot[1,2] = peb$Ep[param_i]
    } else if (param_i == index_param[6]) {
      data_plot[3,2] = peb$Ep[param_i]
    } else if (param_i == index_param[7]) {
      data_plot[4,2] = peb$Ep[param_i]
    } else if (param_i == index_param[8]) {
      data_plot[6,2] = peb$Ep[param_i]
    } else if (param_i == index_param[9]) {
      data_plot[1,3] = peb$Ep[param_i]
    } else if (param_i == index_param[10]) {
      data_plot[2,3] = peb$Ep[param_i]
    } else if (param_i == index_param[11]) {
      data_plot[5,3] = peb$Ep[param_i]
    } else if (param_i == index_param[12]) {
      data_plot[7,3] = peb$Ep[param_i]
    } else if (param_i == index_param[13]) {
      data_plot[5,4] = peb$Ep[param_i]
    } else if (param_i == index_param[14]) {
      data_plot[6,4] = peb$Ep[param_i]
    } else if (param_i == index_param[15]) {
      data_plot[4,5] = peb$Ep[param_i]
    } else if (param_i == index_param[16]) {
      data_plot[7,5] = peb$Ep[param_i]
    } else if (param_i == index_param[17]) {
      data_plot[7,6] = peb$Ep[param_i]
    } else if (param_i == index_param[18]) {
      data_plot[6,7] = peb$Ep[param_i]
    }

    # display parameter, Ep and Pp
    param_ii = param_i-length(peb$Pnames)
    param_name = peb$Pnames[[param_ii]]

    param = as.data.frame(matrix(NA, nrow = 1, ncol = 5))
    colnames(param) = c("Parameter", "Ep", "Pp")
    
    param[1,1] = param_name
    param[1,2] = round(peb$Ep[param_i], 3)
    param[1,3] = round(peb$Pp[param_i], 3)
    
    # merge tables
    param_table = rbind(param_table, param)
    
  }
    
}

colnames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
rownames(data_plot) = c("SFG","cMFG", "iMFG", "cLIP","iLIP", "cEVC","iEVC")
kbl(round(data_plot, 2)) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

# transform into [-1, 1] matrix
for (row_i in 1:nrow(data_plot)) {
  for (col_i in 1:ncol(data_plot)) {
    if (data_plot[row_i, col_i] > 0) {
      data_plot[row_i, col_i] = 1 }
    else if (data_plot[row_i, col_i] < 0) { 
      data_plot[row_i, col_i] = -1 
    }
  }
}

# plot
data_plot = t(data_plot)
ggcorrplot(as.matrix(data_plot[,ncol(data_plot):1]))

# table
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
kbl(param_table) %>%
kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```








