---
title: "Figures manuscript"
author: "Aniol Santo-Angles"
date: "November 2022"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 6
    toc_float: yes

---
  
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
  

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(png)

```

Connections are defined in matrix form (row as target region, column as source region), with the following regions:

1) superior frontal

2) contralateral middle frontal

3) ipsilateral middle frontal

4) contralateral intraparietal area

5) ipsilateral intraparietal area

6) contralateral early visual

7) ipsilateral early visual

# cross-spectral densities (empirical vs predicted)

Figure S1 in Supplementary Material.

![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(1,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(1,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(1,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(1,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(1,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(1,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(1,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(2,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(2,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(2,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(2,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(3,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(3,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(3,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(4,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(4,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(4,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(5,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(5,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(6,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(6,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_empirical_vs_predicted_csd(7,7).jpg){width=70%}

# Sensitivity analysis

Figures 2 in manuscript, and Figures S2-4 in Supplementary Material.

## feedforward connections

![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(1,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(1,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(1,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(1,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(2,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(2,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(2,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(2,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(3,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(3,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(3,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(3,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(4,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(4,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(5,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(5,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(6,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedforward_A(7,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(1,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(1,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(1,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(1,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(2,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(2,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(2,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(2,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(3,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(3,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(3,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(3,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(4,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(4,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(5,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(5,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(6,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedforward_A(7,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(1,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(1,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(1,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(1,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(2,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(2,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(2,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(2,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(3,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(3,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(3,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(3,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(4,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(4,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(5,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(5,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(6,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedforward_A(7,6).jpg){width=70%}

## feedback connections

![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(1,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(1,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(2,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(3,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(4,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(4,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(4,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(5,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(5,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(5,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(6,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(6,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(6,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(6,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(7,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(7,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(7,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_highprec_avgtime_feedback_A(7,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(1,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(1,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(2,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(3,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(4,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(4,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(4,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(5,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(5,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(5,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(6,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(6,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(6,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(6,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(7,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(7,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(7,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_lowprec_avgtime_feedback_A(7,6).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(1,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(1,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(2,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(3,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(4,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(4,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(4,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(5,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(5,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(5,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(6,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(6,2).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(6,4).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(6,7).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(7,1).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(7,3).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(7,5).jpg){width=70%}
![](/Volumes/Neuroimage/Analysis/BESM/DCM/dcm_github/figures/Figure_sensitivity_swap_avgtime_feedback_A(7,6).jpg){width=70%}

